Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-02-16 manuscript/appendix.Rmd
working on Appendix, folder cleanup

\newpage
#Table S1. Climate variable definitions and sources
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3:4, width = "7cm") 
```

>>>>

\newpage
# Table S1. Climate variable definitions and sources
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3:4, width = "7cm") 
```

\newpage
# Table S_. Comparison of growing season length and mean annual temperature as predictors of FACF.
see [issue #58](https://github.com/forc-db/Global_Productivity/issues/58).

\newpage
# Figure S1. 
![](tables_figures/distribution_all_samples.png)
